% CV
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{fancyhdr,tikz,geometry,hyperref,verbatim}
\usepackage{xeCJK}
\setlength{\headheight}{17pt}
\renewcommand{\headrulewidth}{0pt}
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=1cm}
\usepackage[explicit]{titlesec}

\pagestyle{fancy}
\lhead{}
\chead{}
\rhead{}
\lfoot{\today}
\rfoot{\thepage}
\cfoot{Amanda D. Isadore · Curriculum Vitae}

\definecolor{green}{HTML}{bb0000}
\definecolor{grey}{HTML}{666666}
\color{grey}

\newcommand{\raisedrulefill}[2][0ex]{\leaders\hbox{\rule[#1]{1pt}{#2}}\hfill}

\titleformat{\section}{\huge\bfseries}{\thesection}{1em}{#1\,\raisedrulefill[0.1ex]{1pt}}

\begin{document}

\begin{center}\Huge Amanda D. \textbf{\textcolor{green}{Isadore}}\\
\vspace{1mm}
\small \href{https://github.com/AdalineCooper}{Github} | \href{www.linkedin.com/in/aglingua}{Linkedin}
\end{center}

% EDUCATION
\section*{\textcolor{green}{Edu}cation}
\textbf{\textcolor{green}{The Ohio State University}} \hfill \textcolor{green}{\textit{Columbus, OH}}

\noindent \textsc{B.S.E. Computer Science Engineering \hfill {\textit{Aug. 2020 - Present}}}

\noindent \textsc{M.A. in Chinese Language \& Literature \hfill {\textit{Aug. 2020 - Present}}}

% SKILLS
\section*{\textcolor{green}{Ski}lls}
\textsc{Technical: AWS, Azure, Linux, Python, \LaTeX, MacOS\\
Certifications: Azure Fundamentals, AWS Solutions Architect, LPIC-1, RHCSA\\
Languages: English (native), Chinese (bilingual)}

% WORK EXPERIENCE
\section*{\textcolor{green}{Wor}k Experience}

\noindent \textbf{Cheif Marketing Officer} \hfill \textcolor{green}{\textit{Greensboro, NC}}

\noindent \textsc{The Canine Homestead \hfill {\textit{Apr. 2023 - Present}}}
\vspace{-2mm}
\begin{itemize}
    \setlength{\itemsep}{0cm}
    \setlength{\parskip}{0cm}
    \addtolength{\leftskip}{-5mm}
    \item Grew social media following to over 40,000 followers within 45 days
    \item Created and managed brand package over multiple social media platforms, designed website.
    \item Trained dogs in accordance with LIMA training methods
\end{itemize}

\noindent \textbf{Vice President} \hfill \textcolor{green}{\textit{Columbus, OH}}

\noindent \textsc{Excellent Paper International Consulting \hfill {\textit{Feb. 2021 - 2022}}}
\vspace{-2mm}
\begin{itemize}
    \setlength{\itemsep}{0cm}
    \setlength{\parskip}{0cm}
    \addtolength{\leftskip}{-5mm}
    \item Assisted international students with college applications
    \item Managed workflow for team of writers
    \item Facilitated bilingual Chinese/English meetings with C-suite executives of other education consulting firms for future collaboration opportunities
\end{itemize}

% AGLingua
\noindent \textbf{Freelance Translator} \hfill \textcolor{green}{\textit{Columbus, OH}}

\noindent \textsc{Independent Contractor \hfill {\textit{Dec. 2019 - Present}}}
\vspace{-2mm}
\begin{itemize}
    \setlength{\itemsep}{0cm}
    \setlength{\parskip}{0cm}
    \addtolength{\leftskip}{-5mm}
    \item Translated texts from Mandarin Chinese to English using OmegaT/computer assisted translation software.
\end{itemize}

\begin{comment}
    
% SDAG
\noindent \textbf{Title Specalist} \hfill \textcolor{green}{\textit{Remote}}

\noindent \textsc{Super Deal Auto Group, LLC. \hfill {\textit{Feb. 2020 - Present}}}
\vspace{-2mm}
\begin{itemize}
    \setlength{\itemsep}{0cm}
    \setlength{\parskip}{0cm}
    \addtolength{\leftskip}{-5mm}
    \item Prepared all purchasing documents for new vehicles/trade-ins; posted vehicle sales and purchases.
    \item Used language skills to act as a liaison between the company and government/public businesses.
\end{itemize}

% Solutions Staffing
\noindent \textbf{Staffing Recruiter} \hfill \textcolor{green}{\textit{Columbus, OH}}

\noindent \textsc{Solutions Staffing \hfill {\textit{Aug. 2019 - Jan 2020}}}
\vspace{-2mm}
\begin{itemize}
    \setlength{\itemsep}{0cm}
    \setlength{\parskip}{0cm}
    \addtolength{\leftskip}{-5mm}
    \item Facilitated employment solutions and placement for administrative and warehouse positions.
    % \item Provided top quality talent to clients through contract, contract to hire, and direct placement opportunities for administrative and warehouse positions.
\end{itemize}

% Collections Agent
\noindent \textbf{Collections Agent} \hfill \textcolor{green}{\textit{Clemmons, NC/Greensboro, NC}}

\noindent \textsc{Sheffield Financial/Stern Recovery Services Inc. \hfill {\textit{Aug. 2017 - Jul. 2018/Aug. 2018 - Jul. 2019}}}

\vspace{-2mm}
\begin{itemize}
    \setlength{\itemsep}{0cm}
    \setlength{\parskip}{0cm}
    \addtolength{\leftskip}{-5mm}
    \item Negotiated payment terms for past due accounts in accordance with FDCPA, TCPA and CFPB guidelines
\end{itemize}

% ACADEMIC EXPERIENCE
\section*{\textcolor{green}{Aca}demic Experience}

% POLARIS
\textbf{POLARIS} \hfill \textcolor{green}{\textit{Columbus, OH}}

\noindent \textsc{Ohio State University Physics Department \hfill {\textit{August 2020 - May 2021}}}
\vspace{-2mm}
\begin{itemize}
    \setlength{\itemsep}{0cm}
    \setlength{\parskip}{0cm}
    \addtolength{\leftskip}{-5mm}
    \item Studied the detailed fitting of finite source effects in free-floating planet microlensing events. %Worked under the supervision of a graduate student to study microlensing events.
\end{itemize}

% URSA
\noindent \textbf{URSA} \hfill \textcolor{green}{\textit{Columbus, OH}}

\noindent \textsc{Ohio State University Astronomy Department \hfill {\textit{June 2020 - July 2020}}}
\vspace{-2mm}
\begin{itemize}
    \setlength{\itemsep}{0cm}
    \setlength{\parskip}{0cm}
    \addtolength{\leftskip}{-5mm}
    \item Worked in a group that modeled the mass-radius relationship of exoplanets using python.
\end{itemize}

% TEACHING EXPERIENCE
\section*{\textcolor{green}{Tea}ching Experience}

\textbf{Volunteer Teacher's Assistant (Over 750 in-class hours)} \hfill \textcolor{green}{\textit{Winston-Salem, NC}}

\noindent \textsc{Career Center High School \hfill {\textit{Aug 2017 - June 2019}}}
\vspace{-2mm}
\begin{itemize}
    \setlength{\itemsep}{0cm}
    \setlength{\parskip}{0cm}
    \addtolength{\leftskip}{-5mm}
    %\item .
    \item Supported Chinese I, II, III, IV, and AP students. Coached students on speaking, vocabulary, and grammar.
    \item Helped organize the Chinese New Year celebration for the high school attended by 1,500 students.
\end{itemize}

\end{comment}

% OUTREACH & LEADERSHIP
\section*{\textcolor{green}{Out}reach \& Leadership}

% CAS
% Blog Writer
\noindent \textbf{Blog Writer} \hfill \textcolor{green}{\textit{Remote}}

\noindent \textsc{Personal Website \hfill {\textit{Aug 2017 - Present}}}
\vspace{-2mm}
\begin{itemize}
    \setlength{\itemsep}{0cm}
    \setlength{\parskip}{0cm}
    \addtolength{\leftskip}{-5mm}
    \item Wrote articles on grammar, study tips, and language theory for intermediate Chinese learners
    \item Shared articles via social media to increase public engagement in science and promote
    science communication
\end{itemize}

\noindent \textbf{Outreach Coordinator} \hfill {\textit{\textcolor{green}{Columbus, OH}}}

\noindent \textsc{Columbus Astronomical Society \hfill {\textit{Oct. 2020 - Oct. 2021}}}
\vspace{-2mm}
\begin{itemize}
    \setlength{\itemsep}{0cm}
    \setlength{\parskip}{0cm}
    \addtolength{\leftskip}{-5mm}
    \item Created outreach programs to promote science education in central Ohio.
    \item Managed Columbus Astronomical Society social media and volunteer programs. 
\end{itemize}

%\section*{\textcolor{green}{Cer}tifications}
%\textit{May 2018} \quad Chinese Proficiency Test, Level VI \hfill \textcolor{green}{\textit{Confucious Institute, Beijing, China}}

%\section*{\textcolor{green}{Pub}lic Engagement \& Engineering Projects}

\section*{\textcolor{green}{Pre}sentations \& Invited Talks}

\textit{Nov. 2020 \textbf{Mars: The Red Planet}, Columbus Astronomical Society \hfill \textcolor{green}{Virtual}}

\end{document}
